Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-30 manuscript/manuscript.Rmd
crossref stable point fig

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 8 or 9 for wide ranges of parameter values.
Fig. \ref{fig:tbd} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stX.png}
    \caption{$X$ component of fixed points.}
    \label{fig:stx}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stY.png}
    \caption{$Y$ component of fixed points.}
    \label{fig:sty}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stZ.png}
    \caption{$Z$ component of fixed points.}
    \label{fig:stz}
  \end{subfigure}
\end{figure}

>>>>

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 8 or 9 for wide ranges of parameter values.
Fig. \ref{fig:fixed points} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stX.png}
    \caption{$X$ component of fixed points.}
    \label{fig:stx}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stY.png}
    \caption{$Y$ component of fixed points.}
    \label{fig:sty}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stZ.png}
    \caption{$Z$ component of fixed points.}
    \label{fig:stz}
  \end{subfigure}
  \caption{Numerically-computed fixed points of the three-species deterministic model, eq. \eqref{eq:3d model}.}
  \label{fig:fixed points}
\end{figure}
